Histo of ____

### 2017-07-12 histo_template.rmd
Added clean histo template but unusable in rmarkdown

>>>>

```{r image_loop2, results = 'asis'}
png_images <- gtools::mixedsort(list.files("images/"))  # Stores all the files in the dir images/
for(i in 1:length(png_images)){
    name <- strsplit(png_images[i], "\\.")[[1]][1]  # Splits up the string by "." and stores the first part (to get rid of .png)
    cat("\begin{frame}", "\n", 
  cat("### ", strsplit(dickpics[i], "\\.")[[1]][1], "\n", '\\includegraphics[width=\\linewidth,height=\\textheight,keepaspectratio]{{"', file.path("images", strsplit(dickpics[i], "\\.")[[1]][1]), '"}.PNG}', "\n", "\n", sep = "")
}
```
